---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(DT)
```

# ediblecity

<!-- badges: start -->
[![R-CMD-check](https://github.com/icra/edibleCity/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/icra/edibleCity/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of ediblecity is to is to estimate the potential of UA to contribute to addressing several urban challenges at the city-scale. Within this aim, we followed the urban challenges defined by the Eklipse project that are followed for nearly all of the European projects focused on Nature-based Solutions. We selected 8 indicators directly related to one or several urban challenges.

## Installation

You can install the development version of ediblecity from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("icra/edibleCity")
```

## Set a scenario

Although `ediblecity` can also esimate indicators directly from an `sf` object, the function `set_scenario` provides a basic tool to create an scenario combining different proportions of elements of urban agriculture. Some warnings are triggered when the function can't satisfy the parametres passed by the user.

```{r example}
library(ediblecity)

scenario <- set_scenario(city_example,
                         pGardens = 0.7,
                         pVacant = 0.8,
                         pRooftop = 0.6,
                         pCommercial = 0.5)
```
All attributes of urban agriculture elements are included in `city_functions` dataframe. This can be used as default or a customized dataframe can be provided to each indicator.

```{r city_functions}

datatable(city_functions)

```

